Bitmap Indexing for Fast Analysis of Large Astrophysical Datasets

### 2016-09-01 ms/ms.tex
Changed names of figures to standards.

\makeatletter

@@

\author{Meagan~Lang~and~Matthew~Turk}
\thanks{Manuscript received Sept. 1, 2016. This publication is supported in part by the Gordon and Betty Moore Foundation'۪s Data-Driven Discovery Initiative through Grant GBMF4561 to Matthew
Turk. This material is based upon work supported by the National Science
Foundation under Grant No.~ACI-1535651. }
\thanks{The authors are with the National Center for Supercomputing Application, University of Illinois, Urbana-Champaign, IL 61801 USA (e-mail: langmm@illinois.edu)}

@@

%\maketitle

@@

\maketitle
%\IEEEpeerreviewmaketitle

@@

%---------------------------------------------------------------------------------
% DOMAIN DECOMP (682 words)
\subsection{Domain Partitioning Between Files}\label{SS:decomp}
A common analysis task is the selection of data within a subset of the full domain; we use the term ``selector" to refer to the selection operator. If the dataset is split across multiple files, either due to size constraints or to allow for parallel I/O, such selections require every file to be loaded and parsed in order to assemble all of the data within the selection criteria. This process can be very costly in terms of both the memory required to store the data and the time required to read each file. However, if the contents of the files are mapped in advanced, only the files touched by the selection will need to be loaded. This is particularly effective for partitioning schemes that are localized within the domain. If each file contains data that are localized to one part of the domain, selections of contiguous sub-sections within the domain will require fewer files to be loaded. Figure \ref{fig:files} shows four examples of possible partitions of a two-dimensional spatial domain split equally between 8 files. 
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/files.png}
	\caption{Examples of four different schemes for partitioning a 2D domain between 8 files. Each 	color represents a different file.}
	\label{fig:files}
	\end{center}
	\end{figure}
\fi
%

@@

Figure \ref{fig:selectors} shows examples of three selections within the above domain partitions. 
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/selector1.png}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/selector5.png}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/selector4.png}
	\caption{Examples of file selection for four different domain partitions and three different shaded 	selectors. The number of files above each images is the number of files that must be loaded in order to get all of the data within the selected region.}
	\label{fig:selectors}
	\end{center}
	\end{figure}
\fi
%
For the smallest selector (first row), the random domain decomposition (a) already requires half of the files to be loaded while more localized schemes require much fewer. Similarly, while the sliced domain partition (b), requires the fewest files to be loaded when the selector is oriented in the same direction as the slicing (second row), it requires \textit{all} of the files when the selector is perpendicular to the slicing (third row). While some datasets may have information on the domain range covered by each file, the partitioning scheme used for simulation output is often decided at runtime, can be system dependent, and may be imperfect.

@@

%---------------------------------------------------------------------------------
% MORTON INDICES
\subsection{Morton Indices}
Morton ordering maps multidimensional data onto a one-dimensional space filling curve \citep{Morton1996}. This is done by breaking up the domain into cells where each cell's position within the $N$-dimensional domain can be described by $N$ integers. The Morton index of the cell is then created by interleaving the bits of the $N$ integers to create a single integer that fully describes the cell's position (see panel (b) Figure \ref{fig:zorder}). As seen in panel (a) of Figure \ref{fig:zorder}, ordering of the cells by their Morton indices forms a space filling Z-curve.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/zorder.png}
	\caption{Example of 3rd order Morton curve in two dimensions. The bits of the $x$ and $y$ indices are interleaved to generate a single integer that fully describes the cell's location within the two-dimensional domain to within $1/2^{3}$th of the domain in each dimension.}
	\label{fig:zorder}
	\end{center}
	\end{figure}
\fi
%

@@

%---------------------------------------------------------------------------------
% COLLISIONS
\subsection{Collisions}
It is possible that two files will contain data within the same Morton cell.  This would mean that any time that cell is touched by a selection, both files would need to be loaded even if the selection only touches data from one of the files. Figure \ref{fig:collision} provides an example of collisions between two files. In panel (a) of Figure \ref{fig:collision}, purple cells are those that contain data from both files, a collision, for a 3rd order Morton index. Any selector that contained one of those cells would need to load all of the data from both files, even if it only selected part of the cell.  Where the data is highly-concentrated in a central region (for instance, in a galaxy formation simulation with particles centrally-concentrated) this can mean that some regions suffer from worst-case scenario collision.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/collisions.png}
	\caption{Examples of a collision between two files. The red points and blue points are contained by two different files. The larger grid in both panels denotes the boundaries of 3rd order Morton cells.  The cells containing points from either file are shaded accordingly such that cells containing points from both files are purple. The smaller grids within these cells on the right are the boundaries of 2nd order Morton cells refining the collisions.}
	\label{fig:collision}
	\end{center}
	\end{figure}
\fi
%

@@

Collisions are more common for file partitioning schemes that are not localized. Figure \ref{fig:collision_files} shows an example of collisions for the different partitioning schemes discussed in \S\ref{SS:decomp}.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/index.png}
	\caption{Examples of collisions for four different domain partitioning schemes. The heavy black lines denote 1st order Morton cells. The presence of more that one file (color) within a Morton cell indicates a collision.}
	\label{fig:collision_files}
	\end{center}
	\end{figure}
\fi
%
For the random domain partition in panel (a), every cell within a 1st order Morton index will contain data from all 8 files. This means that any selection using a 1st order bitmap index will require every file to be loaded. For the more localized partitions in panels (c) and (d), only two files touch each Morton cell.

@@

Depending on how the domain is split between files, the inclusion of ghost zones may or may not increase the number of files that need to be loaded. Figure \ref{fig:ghosts} shows an example of a ghost zone around the first selector from Figure \ref{fig:selectors}. 
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/ghosts.png}
	\caption{Examples of a selector ghost zone with a width of one Morton cell at an index order of 3 for  four different domain partitioning schemes. The shaded circular region is the selector and the shaded box is the ghost zone. Different partitioning schemes will lead to different numbers of ghost files.}
	\label{fig:ghosts}
	\end{center}
	\end{figure}
\fi
%
The ghost zone has a width of one Morton cell at an index order of 3 and contains the same part of the domain in each case. However, due to differences in how the domain was partitioned between the files in the four cases, the number of additional ghost files touched by the ghost zone in each case is different. This will also depend on the order of the index to which ghost zones are added. Ghost zones added at the order of the coarse index will be larger than those added at the order of the refined index and will have a higher probability of touching additional files. While including ghost zones is advantageous when neighbor info is needed, it also increases the computational cost of identifying files (see \S\ref{S:tests}).

@@

% INDEX ORDER
% TOTAL REFINEMENT
\subsection{Index Order}\label{SS:test_order}
\subsubsection{Overall Refinement}\label{SSS:test_order1}
The order of the Morton indices used to map the files determines the time required to identify files and the number of collisions that will occur between files. Higher order indices will result in fewer collisions, but will take longer to query, as seen in Figure \ref{fig:test_order1}. Six selectors of varying sizes and positions within the domain where used to identify files based on Morton index bitmaps of varying order. The test dataset was split across the files using a Hilbert curve of order 6 with 10\% scatter between Hilbert cells to simulate an imperfect domain decomposition as can occur if particle positions are updated and output prior to updating the domain decomposition.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/vary_order1_or0.png}
	\caption{Dependence of query time (top), fraction of files selected/cells with collisions (middle), and index size (bottom) on the total refinement of the bitmap index. The solid black lines correspond to the query times and files identified by just the selectors. The dashed blue lines correspond to the query times and additional files selected when a ghost zone with the width of one Morton cell is added around the selectors. The dash-dotted line in the middle panel shows the fraction of cells with collisions between files.}
	\label{fig:test_order1}
	\end{center}
	\end{figure}
\fi
%

@@

% SECONDARY REFINEMENT
\subsubsection{Collision Refinement}\label{SSS:test_order2}
Increasing the refinement of the primary index does so for the entire domain and, as seen in \S\ref{SSS:test_order1}, can become costly in terms of the memory required to store the bitmap and the time required to perform operations. However, it is also possible to increase refinement by nesting a second Morton bitmap index within those cells of the primary index that contain collisions. As the nested indexes will contain a smaller portion of the domain and data, they will be less complex and can be compressed more efficiently than the primary index covering the entire domain. This enhanced compression mean that, although a greater overall number of EWAH compressed bitmaps will need to be utilized (one for the coarse index and one for each collision within the coarse index), less space will be needed to store the bitmap and bitwise operations will be faster. Figure \ref{fig:test_order2} shows the results for adding a secondary index of varying order with the overall refinement order of the index (primary index order + secondary index order) held constant at 6. The test dataset and selectors applied were the same as in \S\ref{SSS:test_order1}.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/vary_order2_to6.png}
	\caption{Dependence of query time (top), fraction of files selected/cells with collisions (middle), and memory required to store the index (bottom) on the order of the secondary index used to refine collisions. In the middle panel, the solid black line corresponds with the fraction of files identified, the dash-dotted blue line is the fraction of cells at the first index level that have collisions, and the dotted red line is the fraction of cells at the second index level that have collisions.}
	\label{fig:test_order2}
	\end{center}
	\end{figure}
\fi
%

@@

% SELECTOR SIZE
\subsection{Selector Size}\label{SS:test_size}
%
The time required to identify files touched by a selection will also depend upon the size of the region being selected. Larger selectors will intersect more indices and more files, resulting in more bitmap operations. Figure \ref{fig:test_size} shows the result from varying the selector size. The same test data set from \S\ref{SS:test_order} was used. A bitmap index with a 4th order primary Morton index and 2nd order secondary Morton index was used in all cases. Each cube selector was placed at the center of the domain and scaled along each dimension to some fraction of the total domain.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/vary_selector.png}
	\caption{Dependence of query time (top) and number of files selected (bottom) on selector width in terms of the total domain width. The solid black lines correspond to the query times and files identified by the selectors alone. The dashed blue lines correspond the query times and additional files identified when a ghost zone with a width of one cell is added to the selector.}
	\label{fig:test_size}
	\end{center}
	\end{figure}
\fi
%

@@

% DOMAIN DECOMP
\subsection{Domain Partitioning}\label{SS:test_decomp}
%
As discussed in \S\ref{SS:decomp}, a bitmap index is more effective in cases where the domain is partitioned between files in a localized way. If files contain non-contiguous parts of the domain, contiguous selections will require more files to be loaded. Figure \ref{fig:test_decomp} shows results for four different partitioning schemes. All four data sets cover the same three-dimensional domain with $1024^3$ points split across 512 files. The Hilbert dataset is the same one used in previous tests (see \S\ref{SS:test_order} for a description). The Morton dataset is constructed in a similar way to the Hilbert dataset with file partitions occurring along a 6th order Morton curve and including a 10\% scatter of points between Morton cells. The sliced dataset is partitioned in slices along one dimension with 10\% scatter of points between adjacent slices. Files in the random dataset contain a random sample of points, uniformly distributed across the domain.
%
\ifinclfig
	\begin{figure}[hbpt]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/vary_decomp_to0.png}
	\caption{Dependence of query time (top), the number of files selected (middle), and the size of the index (bottom) on index order for different domain partitioning between files. The dotted magenta lines are for a randomly partitioned dataset, the cyan dashed-dotted lines are a dataset partitioned by equal slices alone one dimension, the dashed red lines are a dataset partitioned along an 6th order Morton curve, and the solid blue lines are a dataset partitioned along a 6th order Hilbert curve.}
	\label{fig:test_decomp}
	\end{center}
	\end{figure}
\fi
%

>>>>

%\makeatletter

@@

\author{Meagan~Lang~and~Matthew~Turk%
\thanks{Manuscript received Sept. 1, 2016. This publication is supported in part by the Gordon and Betty Moore Foundation'۪s Data-Driven Discovery Initiative through Grant GBMF4561 to Matthew
Turk. This material is based upon work supported by the National Science
Foundation under Grant No.~ACI-1535651. }%
\thanks{The authors are with the National Center for Supercomputing Application, University of Illinois, Urbana-Champaign, IL 61801 USA (e-mail: langmm@illinois.edu)}}

@@

\maketitle

@@

\IEEEpeerreviewmaketitle

@@

%---------------------------------------------------------------------------------
% DOMAIN DECOMP (682 words)
\subsection{Domain Partitioning Between Files}\label{SS:decomp}
A common analysis task is the selection of data within a subset of the full domain; we use the term ``selector" to refer to the selection operator. If the dataset is split across multiple files, either due to size constraints or to allow for parallel I/O, such selections require every file to be loaded and parsed in order to assemble all of the data within the selection criteria. This process can be very costly in terms of both the memory required to store the data and the time required to read each file. However, if the contents of the files are mapped in advanced, only the files touched by the selection will need to be loaded. This is particularly effective for partitioning schemes that are localized within the domain. If each file contains data that are localized to one part of the domain, selections of contiguous sub-sections within the domain will require fewer files to be loaded. Figure \ref{fig:files} shows four examples of possible partitions of a two-dimensional spatial domain split equally between 8 files. 
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang1.png}
	\caption{Examples of four different schemes for partitioning a 2D domain between 8 files. Each 	color represents a different file.}
	\label{fig:files}
	\end{center}
	\end{figure}
\fi
%

@@

Figure \ref{fig:selectors} shows examples of three selections within the above domain partitions. 
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang2a.png}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang2b.png}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang2c.png}
	\caption{Examples of file selection for four different domain partitions and three different shaded 	selectors. The number of files above each images is the number of files that must be loaded in order to get all of the data within the selected region.}
	\label{fig:selectors}
	\end{center}
	\end{figure}
\fi
%
For the smallest selector (first row), the random domain decomposition (a) already requires half of the files to be loaded while more localized schemes require much fewer. Similarly, while the sliced domain partition (b), requires the fewest files to be loaded when the selector is oriented in the same direction as the slicing (second row), it requires \textit{all} of the files when the selector is perpendicular to the slicing (third row). While some datasets may have information on the domain range covered by each file, the partitioning scheme used for simulation output is often decided at runtime, can be system dependent, and may be imperfect.

@@

%---------------------------------------------------------------------------------
% MORTON INDICES
\subsection{Morton Indices}
Morton ordering maps multidimensional data onto a one-dimensional space filling curve \citep{Morton1996}. This is done by breaking up the domain into cells where each cell's position within the $N$-dimensional domain can be described by $N$ integers. The Morton index of the cell is then created by interleaving the bits of the $N$ integers to create a single integer that fully describes the cell's position (see panel (b) Figure \ref{fig:zorder}). As seen in panel (a) of Figure \ref{fig:zorder}, ordering of the cells by their Morton indices forms a space filling Z-curve.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang3.png}
	\caption{Example of 3rd order Morton curve in two dimensions. The bits of the $x$ and $y$ indices are interleaved to generate a single integer that fully describes the cell's location within the two-dimensional domain to within $1/2^{3}$th of the domain in each dimension.}
	\label{fig:zorder}
	\end{center}
	\end{figure}
\fi
%

@@

%---------------------------------------------------------------------------------
% COLLISIONS
\subsection{Collisions}
It is possible that two files will contain data within the same Morton cell.  This would mean that any time that cell is touched by a selection, both files would need to be loaded even if the selection only touches data from one of the files. Figure \ref{fig:collision} provides an example of collisions between two files. In panel (a) of Figure \ref{fig:collision}, purple cells are those that contain data from both files, a collision, for a 3rd order Morton index. Any selector that contained one of those cells would need to load all of the data from both files, even if it only selected part of the cell.  Where the data is highly-concentrated in a central region (for instance, in a galaxy formation simulation with particles centrally-concentrated) this can mean that some regions suffer from worst-case scenario collision.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang4.png}
	\caption{Examples of a collision between two files. The red points and blue points are contained by two different files. The larger grid in both panels denotes the boundaries of 3rd order Morton cells.  The cells containing points from either file are shaded accordingly such that cells containing points from both files are purple. The smaller grids within these cells on the right are the boundaries of 2nd order Morton cells refining the collisions.}
	\label{fig:collision}
	\end{center}
	\end{figure}
\fi
%

@@

Collisions are more common for file partitioning schemes that are not localized. Figure \ref{fig:collision_files} shows an example of collisions for the different partitioning schemes discussed in \S\ref{SS:decomp}.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang5.png}
	\caption{Examples of collisions for four different domain partitioning schemes. The heavy black lines denote 1st order Morton cells. The presence of more that one file (color) within a Morton cell indicates a collision.}
	\label{fig:collision_files}
	\end{center}
	\end{figure}
\fi
%
For the random domain partition in panel (a), every cell within a 1st order Morton index will contain data from all 8 files. This means that any selection using a 1st order bitmap index will require every file to be loaded. For the more localized partitions in panels (c) and (d), only two files touch each Morton cell.

@@

Depending on how the domain is split between files, the inclusion of ghost zones may or may not increase the number of files that need to be loaded. Figure \ref{fig:ghosts} shows an example of a ghost zone around the first selector from Figure \ref{fig:selectors}. 
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang6.png}
	\caption{Examples of a selector ghost zone with a width of one Morton cell at an index order of 3 for  four different domain partitioning schemes. The shaded circular region is the selector and the shaded box is the ghost zone. Different partitioning schemes will lead to different numbers of ghost files.}
	\label{fig:ghosts}
	\end{center}
	\end{figure}
\fi
%
The ghost zone has a width of one Morton cell at an index order of 3 and contains the same part of the domain in each case. However, due to differences in how the domain was partitioned between the files in the four cases, the number of additional ghost files touched by the ghost zone in each case is different. This will also depend on the order of the index to which ghost zones are added. Ghost zones added at the order of the coarse index will be larger than those added at the order of the refined index and will have a higher probability of touching additional files. While including ghost zones is advantageous when neighbor info is needed, it also increases the computational cost of identifying files (see \S\ref{S:tests}).

@@

% INDEX ORDER
% TOTAL REFINEMENT
\subsection{Index Order}\label{SS:test_order}
\subsubsection{Overall Refinement}\label{SSS:test_order1}
The order of the Morton indices used to map the files determines the time required to identify files and the number of collisions that will occur between files. Higher order indices will result in fewer collisions, but will take longer to query, as seen in Figure \ref{fig:test_order1}. Six selectors of varying sizes and positions within the domain where used to identify files based on Morton index bitmaps of varying order. The test dataset was split across the files using a Hilbert curve of order 6 with 10\% scatter between Hilbert cells to simulate an imperfect domain decomposition as can occur if particle positions are updated and output prior to updating the domain decomposition.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang7.png}
	\caption{Dependence of query time (top), fraction of files selected/cells with collisions (middle), and index size (bottom) on the total refinement of the bitmap index. The solid black lines correspond to the query times and files identified by just the selectors. The dashed blue lines correspond to the query times and additional files selected when a ghost zone with the width of one Morton cell is added around the selectors. The dash-dotted line in the middle panel shows the fraction of cells with collisions between files.}
	\label{fig:test_order1}
	\end{center}
	\end{figure}
\fi
%

@@

% SECONDARY REFINEMENT
\subsubsection{Collision Refinement}\label{SSS:test_order2}
Increasing the refinement of the primary index does so for the entire domain and, as seen in \S\ref{SSS:test_order1}, can become costly in terms of the memory required to store the bitmap and the time required to perform operations. However, it is also possible to increase refinement by nesting a second Morton bitmap index within those cells of the primary index that contain collisions. As the nested indexes will contain a smaller portion of the domain and data, they will be less complex and can be compressed more efficiently than the primary index covering the entire domain. This enhanced compression mean that, although a greater overall number of EWAH compressed bitmaps will need to be utilized (one for the coarse index and one for each collision within the coarse index), less space will be needed to store the bitmap and bitwise operations will be faster. Figure \ref{fig:test_order2} shows the results for adding a secondary index of varying order with the overall refinement order of the index (primary index order + secondary index order) held constant at 6. The test dataset and selectors applied were the same as in \S\ref{SSS:test_order1}.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang8.png}
	\caption{Dependence of query time (top), fraction of files selected/cells with collisions (middle), and memory required to store the index (bottom) on the order of the secondary index used to refine collisions. In the middle panel, the solid black line corresponds with the fraction of files identified, the dash-dotted blue line is the fraction of cells at the first index level that have collisions, and the dotted red line is the fraction of cells at the second index level that have collisions.}
	\label{fig:test_order2}
	\end{center}
	\end{figure}
\fi
%

@@

% SELECTOR SIZE
\subsection{Selector Size}\label{SS:test_size}
%
The time required to identify files touched by a selection will also depend upon the size of the region being selected. Larger selectors will intersect more indices and more files, resulting in more bitmap operations. Figure \ref{fig:test_size} shows the result from varying the selector size. The same test data set from \S\ref{SS:test_order} was used. A bitmap index with a 4th order primary Morton index and 2nd order secondary Morton index was used in all cases. Each cube selector was placed at the center of the domain and scaled along each dimension to some fraction of the total domain.
%
\ifinclfig
	\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang9.png}
	\caption{Dependence of query time (top) and number of files selected (bottom) on selector width in terms of the total domain width. The solid black lines correspond to the query times and files identified by the selectors alone. The dashed blue lines correspond the query times and additional files identified when a ghost zone with a width of one cell is added to the selector.}
	\label{fig:test_size}
	\end{center}
	\end{figure}
\fi
%

@@

% DOMAIN DECOMP
\subsection{Domain Partitioning}\label{SS:test_decomp}
%
As discussed in \S\ref{SS:decomp}, a bitmap index is more effective in cases where the domain is partitioned between files in a localized way. If files contain non-contiguous parts of the domain, contiguous selections will require more files to be loaded. Figure \ref{fig:test_decomp} shows results for four different partitioning schemes. All four data sets cover the same three-dimensional domain with $1024^3$ points split across 512 files. The Hilbert dataset is the same one used in previous tests (see \S\ref{SS:test_order} for a description). The Morton dataset is constructed in a similar way to the Hilbert dataset with file partitions occurring along a 6th order Morton curve and including a 10\% scatter of points between Morton cells. The sliced dataset is partitioned in slices along one dimension with 10\% scatter of points between adjacent slices. Files in the random dataset contain a random sample of points, uniformly distributed across the domain.
%
\ifinclfig
	\begin{figure}[hbpt]
	\begin{center}
	\includegraphics[width=\columnwidth,keepaspectratio]{../images/lang10.png}
	\caption{Dependence of query time (top), the number of files selected (middle), and the size of the index (bottom) on index order for different domain partitioning between files. The dotted magenta lines are for a randomly partitioned dataset, the cyan dashed-dotted lines are a dataset partitioned by equal slices alone one dimension, the dashed red lines are a dataset partitioned along an 6th order Morton curve, and the solid blue lines are a dataset partitioned along a 6th order Hilbert curve.}
	\label{fig:test_decomp}
	\end{center}
	\end{figure}
\fi
%
